NEED TITLE

### 2015-01-13 ms.tex
Brought geometry.pdf files to paper- need captions
Add Mdot, & disc. more mass. region & start less

In prior work, we examined the geometry of accretion, i.e., does the accretion proceed along filament or over 4$\pi$ steradian, by plotting the cumulative accretion rate as a function of density. In Figure \ref{fig:accretion average rho}, we plot the cumulative accretion rate as a function of density, normalized to the average density in shells of radii 0.5 (upper plots) and 0.02 pc (lower plots).  Plots on the left are associated with the more massive star forming region, where 3 star particles reside and plots on the right are associated with the less massive star forming region, where two star particles reside.  The density where 50\% of the accretion is accounted for occurs at $\rho/\bar{\rho} \approx 3$ for the more massive star forming region and appears to be independent of whether the shell has a radius of 0.5 or 0.02 pc.  On the other hand, the less massive star forming region has half of the accretion account for at $\rho/\bar{\rho} \approx 10$ at r=0.5 pc.  This suggests that the accretion is directed along filaments.  This filamentary nature of accretion does not maintain itself to lower radii, where at 0.02 pc, the 50\% point in cumulatiove accertion occurs at $\rho/\bar{\rho} \approx 1$, which suggest accretion along $4\pi$ steradian.
{\bf INCLUDE ACCRETION TOPOLOGY STUDY HERE.}

@@

@@

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we compare radially averaged profiles around these high density points to their analytic theory.  In the left panel of Figure \ref{fig:good_rho_example}, we show the radial density profile around one such high density point. As this figure shows, the radial density profile follows a $r^{-3/2}$ power law in agreement with analytic expections.  This power-law breaks down at small radii, but this is not unexpected as this radii corresponds to the presents of a rotationally support disk.  Such good agreement is not universal for all high density points as shown in the right panel of Figure \ref{fig:bad_rho_example}.  Here the radial density profile follows a $r^{-2}$ power law.  
%\begin{figure*}
%\plottwo{Track_0256_000_rho.png}{Track_0132_000_rho.png}
%\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and declines to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. \label{fig:good_rho_example}
%{bf\ This discusses left panel only, should we move the discussion outside the caption?}}
%\end{figure*}

@@

\begin{figure*}
\plottwo{Disk_0132_0000.png}{Track_0132_000_rho.png}
\plottwo{Track_0132_000_vr.png}{Track_0132_000_mass.png}
\plottwo{Track_0132_000_mass.png}{pdf_frame_0132_0000.png}
\caption{Tracking 132 000  These plots show various data for one of the particles formed in the simulation.  The upper left graph shows the density profile, with reference lines indicating slopes of -3/2, -2, and -5/2.  The slope between $0.02$pc and $0.4$pc approximately matches the -5/2 reference line.  The plot on the upper right shows the pdf function related to volumes of 1pc, 2pc, and 5pc.  The bottom left shows a plot of the radial velocity and turbulent velocity associated with the particle.  The lower right graph shows the radial density profile of the particle.    \label{fig:132 000 graphs}}
\end{figure*}

\begin{figure*}
\plottwo{Disk_0132_0002.png}{Track_0132_002_rho.png}
\plottwo{Track_0132_002_vr.png} {Track_0132_002_mass.png}
\plottwo{Track_0132_002_mass.png}{pdf_frame_0132_0002.png}
\caption{Tracking 132 002  These plots show the data for a different particle formed in the simulation at the same time as the previous plots.  The upper left graph of the density in the region neatly matches the -3/2 slope.  The pdf graph in the upper right again shows the plots for volumes related to $1$pc, $2$pc, and $5$pc.  The lower left plot demonstrates the loose connection between the radial velocity and the turbulent velocity.  The graph on the lower right again shows the density profile of this second particle.     \label{fig:132_002_graphs}}
\end{figure*}

>>>>

@@

In prior work, we examined the geometry of accretion, i.e., does the accretion proceed along filament or over 4$\pi$ steradian, by plotting the cumulative accretion rate as a function of density. In Figure \ref{fig:accretion average rho}, we plot the cumulative accretion rate as a function of density, normalized to the average density in shells of radii 0.5 (upper plots) and 0.02 pc (lower plots).  Plots on the left are associated with the more massive star forming region, where 3 star particles reside and plots on the right are associated with the less massive star forming region, where two star particles reside.  The density where 50\% of the accretion is accounted for occurs at $\rho/\bar{\rho} \approx 3$ for the more massive star forming region and appears to be independent of whether the shell has a radius of 0.5 or 0.02 pc.  This suggests that the accretion is proceeding along filaments.  Similarly, the less massive star forming region has half of the accretion account for at $\rho/\bar{\rho} \approx 10$ at r=0.5 pc, again suggesting filamentary accretion.  However, this filamentary nature of accretion does not maintain itself to lower radii, where at 0.02 pc, the 50\% point in cumulatiove accertion occurs at $\rho/\bar{\rho} \approx 1$, which suggest accretion is spherical.

Figures \ref{fig:geometry} and \ref{fig:geometry 2} show the moments of inertia for the three star particles in the more massive and less massive star forming regions, respectively.  For the more massive star forming region (Fig. \ref{fig:geometry}), note that the moments of inertia are identical for radii greater than $2e-2$, due the fact that these three star particles sit in the same massive star forming region. This is similarly true for the less massive region for $r\gtrsim 0.1$ pc.  At small radii, the distribution of gas appears to be flattened or rod-like, which is implied by the relative values of the three principle axes.  Around $r\approx 0.02$ and $r \approx 0.1$ pc, respectively, the geometry of the gas is relatively spherical.  Outside this region, the gas become flatter again. However, the flattened distributions seen at small and larger radii may also reflect the effect of streams of gas or gravitational instabilities that are associated with the accretion.

\begin{figure}
\plotone{geometry_4_cum.pdf}
\caption{Plots of the moments of inertia for the three star particles in the more massive star forming region.  Note that the moments of inertia are identical for radii greater than $2e-2$, due the fact that these three star particles sit in the same massive star forming region.  Inside this region, we find that the two largest moments of inertia are close in value to each other, suggesting that the geometry of the gas resembles a flattened distribution. Around $r\approx 0.02$ pc, the geometry of the gas becomes relatively spherical.  Outside this region, the gas become flatter again. However, the flattened distributions seen at small and larger radii may also reflect the effect of streams of gas that might drive the accretion. 
\label{fig:geometry}}
\end{figure}

\begin{figure}
\plotone{geometry_4_cum.pdf}
\caption{$Geometry_2$ and $geometry_4$ Plots of the moments of inertia for the two star particles in the less massive star forming region.  The moments of inertia for these particles are identical down to a radius of $r\approx 0.1$ pc
\label{fig:geometry 2}}
\end{figure}

@@

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we proceed to compare radially averaged profiles around these high density points to their analytic theory.  Toward this end, we construct radial profiles around the most massive star particle in each of the star forming regions.

In Figure \ref{fig:132 000 graphs}, we show the radial distribution of $\rho$, $v_r$, $v_t$, $M(r)$, $\dot{M}$, and the density distribution function around the three star particles.  In the top left plot, we show a slice of the region perpendicular to the z-axis.  The top right plot shows $\rho(r)$ alongside lines of $r^{-3/2}$, $r^{-2}$ and $r^{-5/2}$.  Here we find that at small radii, $\rho(r)\sim r^{-2}$ at small radii and $\rho(r) \sim r^{-3/2}$ between 0.1 - 1 pc. At other radii, the density profile is surprisingly steep, steeper than even $r^{-5/2}$.

The velocity profiles show similar change in behavior in the transition increasing from small radii, around $r\approx 0.02$ pc.  The radial velocity tends to increase to $0.02$ pc, and then decreases following the slope noted in the red line of 0.5.  This demarcation from the smaller radii to larger is due to the disk-like shape of the star particle at the smaller radii.  The turbulent velocity, green line, decreases inward.

The middle right graph shows the mass as a function of radius.  The mass monotonically increases.  However there is a flattening around $0.1$ pc before it steepens again.  This is important because this region behaves similarly to a point mass.  Which is also reflected in the density profile and the radial velocity profile where $\rho \sim r^-1.5$ and $v_r \sim r^{-1/2}$ as shown by MC15 around point masses.

The bottom left graph shows the mass accretion rates for all three particles in the more massive region.  At small radii, the drop off in $\dot M$ is due to the presence of a disk, the drop off at larger radii is due to the step density profile.

The bottom right graph depicts the density PDF for three different radii.  Here it roughly corresponds to the density profile shown in the top right plot.  For instance, the PDF inside a 1 pc sphere has a slope of $\rho ^-1.3$ which corresponds to a radial profile of $\rho \sim r^-2.5$, whereas for a 2 pc sphere, the slope is now $\rho ^-1.5$ corresponding to radial profile of $\rho \sim r^-2$.

The comparative plots for the less massive region are shown in \ref{fig:132_002_graphs}.  The upper left graph shows a slice perpendicular to the z axis in the plane of peak density.  The graph shows a single filamentary strand of accretion towards the inner disk-like structure.

Here again the top right plot shows $\rho(r)$ alongside lines of $r^{-3/2}$, $r^{-2}$ and $r^{-5/2}$.  In this instance, however, the slope of $\rho(r)$ is approximately $r^-2$ for $r \gtrsim 0.1$ pc as well as for $r \lesssim 5e-3$ pc.  Between radii $r \eqsim 0.01$ pc and $r \eqsim 0.1$ pc, $\rho$ closely matches the slope of $r^{-3/2}$.  There is also a sharp spike in density at $r = 6e-3$ pc that is notable in the mass plot as well.

%In the left panel of Figure \ref{fig:good_rho_example}, we show the radial density profile around one such high density point. As this figure shows, the radial density profile follows a $r^{-3/2}$ power law in agreement with analytic expections.  This power-law breaks down at small radii, but this is not unexpected as this radii corresponds to the presents of a rotationally support disk.  Such good agreement is not universal for all high density points as shown in the right panel of Figure \ref{fig:bad_rho_example}.  Here the radial density profile follows a $r^{-2}$ power law.  
%\begin{figure*}
%\plottwo{Track_0256_000_rho.png}{Track_0132_000_rho.png}
%\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and declines to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. \label{fig:good_rho_example}
%{bf\ This discusses left panel only, should we move the discussion outside the caption?}}
%\end{figure*}

@@

\begin{figure*}
\plottwo{Disk_0132_0000.png}{Track_0132_000_rho.png}
\plottwo{Track_0132_000_vr.png}{Track_0132_000_mass.png}
\plottwo{Track_0132_003_mdot.png}{pdf_frame_0132_0000.png}
\caption{Tracking 132 000  These plots show various data for one of the particles formed in the more massive region in the simulation.  The upper left plot shows the zoomed out region with radius of $1.5$ pc. The upper right graph shows the density profile for one of the particles in the region with reference lines indicating slopes of $-5/2$, $-2$, and $-3/2$.  The slope between $0.02$pc and $0.4$pc approximately matches the $-5/2$ reference line.  The middle left shows a plot of the radial velocity and turbulent velocity associated with the particle.    The middle right graph shows the radial density profile of the particle.  The plot on the lower left compares the mass accretion rates between the three particles in the more massive region.  The accretion rates are very similar at radii greater than $r \approx 10^{-2}$ pc.  The plot on the lower right shows the pdf function related to volumes of 1pc, 2pc, and 5pc.    \label{fig:132 000 graphs}}
\end{figure*}

\begin{figure*}
\plottwo{Disk_0132_0002.png}{Track_0132_002_rho.png}
\plottwo{Track_0132_002_vr.png} {Track_0132_002_mass.png}
\plottwo{Track_0132_004_mdot.png}{pdf_frame_0132_0002.png}
\caption{Tracking 132 002  These plots show the data for a different particle formed in the simulation at the same time as the previous plots.  The upper left graph of the density in the region neatly matches the -3/2 slope.  The pdf graph in the upper right again shows the plots for volumes related to $1$pc, $2$pc, and $5$pc.  The lower left plot demonstrates the loose connection between the radial velocity and the turbulent velocity.  The graph on the lower right again shows the density profile of this second particle.     \label{fig:132_002_graphs}}
\end{figure*}
